### 2014-10-31 docs/ms.Rmd
Changed line endings to have two spaces to start a new paragraph, rather than skipping a line

##Introduction
Since Thayer (1909), Poulton (1890) and Wallace (YEAR) generations of biologists have endeavored to explain the mechanisms and functions of animal and plant coloration. For these biologists, identifying best practice in measuring color and color pattern and in determining how other species see colour has been a great challenge. Over the past 150 years biologists, both independently and in collaboration with physicists and chemists, have sought out and created methods that have enabled some remarkable discoveries (Lythgoe 1979 Shout out to Endler here?). These include, for example, the fundamental differences between human color vision and that of other animals (Bennett 1994) and the ubiquity of ultraviolet coloration in birds (Eaton & Lanyon 2003).

  Today, the range of techniques used in research for measuring coloration are diverse and encompass spectrophotometry (also called spectroradiometry, spectroscopy ETC), photography, visual modeling.
The application of spectrophotometry to questions in ecology and evolution revolutionized the field (Dyck 1966). Before the widespread use of spectrophotometry researchers assigned categorical color descriptions, arbitrary rankings or scores (e.g. Aldrich & James, 1991; Wheelwright & Janson, 1985) or matched paint swatches or munsell chip ratings based on their own visual assessment (e.g. Key and Day 1954, Burtt 1986). Although no doubt applied carefully, these techniques limited progress in field. For example, many researchers designed color assessment methods specifically for their projects (e.g. Alrich and James 1991) rendering data by different researchers incomparable. This was/is especially problematic when different measurement techniques are used on the same species (e,g, refXXX vs ref XXX). Also, human vision, blind to ultraviolet wavelengths, is inherently different to most other animals such as avian and reptilian tetrachromats and insect trichromats, (Bennett 1994, Douglas and Jeffrey 2014); human perception of color, and variation therein, is not only biologically irrelevant to most systems, but it can lead to erroneous conclusions (Bennett, Cuthill and Norris 1994, Endler 1990).

>>>>

##Introduction
Since Thayer (1909), Poulton (1890) and Wallace (YEAR) generations of biologists have endeavored to explain the mechanisms and functions of animal and plant coloration. For these biologists, identifying best practice in measuring color and color pattern and in determining how other species see colour has been a great challenge. Over the past 150 years biologists, both independently and in collaboration with physicists and chemists, have sought out and created methods that have enabled some remarkable discoveries (Lythgoe 1979 Shout out to Endler here?). These include, for example, the fundamental differences between human color vision and that of other animals (Bennett 1994) and the ubiquity of ultraviolet coloration in birds (Eaton & Lanyon 2003). Today, the range of techniques used in research for measuring coloration are diverse and encompass spectrophotometry (also called spectroradiometry, spectroscopy ETC), photography, visual modeling.  
The application of spectrophotometry to questions in ecology and evolution revolutionized the field (Dyck 1966). Before the widespread use of spectrophotometry researchers assigned categorical color descriptions, arbitrary rankings or scores (e.g. Aldrich & James, 1991; Wheelwright & Janson, 1985) or matched paint swatches or munsell chip ratings based on their own visual assessment (e.g. Key and Day 1954, Burtt 1986). Although no doubt applied carefully, these techniques limited progress in field. For example, many researchers designed color assessment methods specifically for their projects (e.g. Alrich and James 1991) rendering data by different researchers incomparable. This was/is especially problematic when different measurement techniques are used on the same species (e,g, refXXX vs ref XXX). Also, human vision, blind to ultraviolet wavelengths, is inherently different to most other animals such as avian and reptilian tetrachromats and insect trichromats, (Bennett 1994, Douglas and Jeffrey 2014); human perception of color, and variation therein, is not only biologically irrelevant to most systems, but it can lead to erroneous conclusions (Bennett, Cuthill and Norris 1994, Endler 1990).   
